14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-11 rules/rules19.tex
Rules: Macro for industry challenge track.

\newcommand{\main}{Single Query\xspace}
\newcommand{\incremental}{Incremental\xspace}
\newcommand{\ucore}{Unsat Core\xspace}
\newcommand{\mval}{Model Validation\xspace}

@@

SMT-COMP 2019 will have five tracks: the \main Track (formerly known
as Main Track), the incremental track (formerly known as application
track), the \ucore Track, the (new) industry challenge track, and the (new)
\mval Track.

@@

The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
pair in the \main, \incremental and \ucore tracks, \todo{XX}~minutes in the
industry challenge track, and \todo{XX}~minutes in the \mval Track
\todo{Need to elaborate how time is split? Do we
need two time limits here, one for solving and one for
validation?}.\footnote{The time limit may be
adjusted once we know the number of competition entrants and eligible
benchmarks.}  Solvers that take more than this time limit will be killed.
Solvers are allowed to spawn other processes; these will be killed at
approximately the same time as the first started process.

@@

\subsection{Industry challenge track}
\label{sec:exec:industry-challenge}

The industry challenge track will follow the same rules as the \main Track,
with two exceptions: benchmark selection and the time limit. The track will run on
all SMT-LIB benchmarks that have an unknown status and that have been tagged as being
 \emph{industrial}. Additionally we will include benchmarks nominated by the community.
\lh{TODO: benchmark selection still needs discussion}
\lh{TODO: We didn't decide on what we do if only one solver gives an answer and we don't
know if the problem is sat/unsat}

>>>>

\newcommand{\main}{Single Query\xspace}
\newcommand{\incremental}{Incremental\xspace}
\newcommand{\ucore}{Unsat Core\xspace}
\newcommand{\mval}{Model Validation\xspace}
\newcommand{\challenge}{Industry Challenge\xspace}

@@

SMT-COMP 2019 will have five tracks: the \main Track (formerly known
as Main Track), the incremental track (formerly known as application
track), the \ucore Track, the (new) \challenge Track, and the (new)
\mval Track.

@@

The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
pair in the \main, \incremental and \ucore tracks, \todo{XX}~minutes in the
\challenge Track, and \todo{XX}~minutes in the \mval Track
\todo{Need to elaborate how time is split? Do we
need two time limits here, one for solving and one for
validation?}.\footnote{The time limit may be
adjusted once we know the number of competition entrants and eligible
benchmarks.}  Solvers that take more than this time limit will be killed.
Solvers are allowed to spawn other processes; these will be killed at
approximately the same time as the first started process.

@@

\subsection{\challenge Track}
\label{sec:exec:industry-challenge}

The \challenge Track will follow the same rules as the \main Track,
with two exceptions: benchmark selection and the time limit. The track will run on
all SMT-LIB benchmarks that have an unknown status and that have been tagged as being
 \emph{industrial}. Additionally we will include benchmarks nominated by the community.
\lh{TODO: benchmark selection still needs discussion}
\lh{TODO: We didn't decide on what we do if only one solver gives an answer and we don't
know if the problem is sat/unsat}
